Exploratory Data Analysis

### 2024-01-11 analysis/aggressive_care.qmd
updates

We want to determine if there's a substantial difference in the proportion of patients who receive neurosurgical intervention in the right or left hemisphere.

```{r color setup}

@@

@@

## Neurosurgical Intervention - Multivariate Regression

@@

@@

>>>>

```{r color setup, warning=FALSE, message=FALSE}

@@

We want to determine if there's a substantial difference in the proportion of patients who receive aggressive care (mostly neurosurgical intervention) in the right vs. left hemisphere.

### Table 2 - Aggressiveness of Care (Unadjusted)

Things to clarify:

- How is comfort care defined?
- Put mean instead of median?
- Run "unadjusted analyses" and put results of both adjusted and unadjusted into one table

@@

### Aggressiveness of Care (Adjusted)

#### Neurosurgical Intervention

@@

#### Days of Mechanical Ventilation

```{r days of ventilation, warning=FALSE, message=FALSE}
#| fig-width: 10

@@

#### Comfort Care

```{r comfort care, warning=FALSE, message=FALSE}
#| fig-width: 10

### 2024-01-11 analysis/eda.qmd
updates

- Collapse some categorical values
- IVH as binary instead of volume
- Some percentages values are off, likely due to missing data (e.g., Hypertension)

>>>>

- Collapse some categorical values especially those that are missing
- Some percentages values are off, likely due to missing data (e.g., Hypertension). Confirm PMH data.
